---
title: "Introduction to R"
author: "Clay Curry"
date: "9/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic Syntax

The statistical programming language **R** uses *functions* to perform operations on *vector* data structures of atomic data types (including Numeric, Character, Logical, Complex, Raw). To access documentation for quick-help, typing `?funcname` will always cause **R** to open a new help file window with additional information about the function `funcname`. A function can have any number of inputs. For example, to create a vector of numbers, we use the function `c()` (for concatenate).

```{r cars}
primes <- c(1,2,3,5,7,11,13,17,19,21,23)

primes
```

Additionally, there are several functions that can show you the data type of an R object
```{r eval=FALSE}
typeof(x)
mode(x)
storage.mode(x)
class(x)
str(x)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
